The role of emotional factors in face processing abilities in Autism Spectrum Conditions

### 2023-07-08 manuscript.Rmd
Added tables

packagelist <- c('pwr')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

knitr::opts_chunk$set(echo = TRUE)

@@

@@

The non-autistic group was recruited via social media, ‘word of mouth’, and via Prolific. We aimed to collect 100 non-autistic participants, and had 119 complete datasets. However, 21 were removed due to being incomplete, or failing an attention check measure. This means that data from a sample of 98 non-autistic adults was been collected in a previous study using the same methods, materials and experimental design. This sample serves as a comparison group to the autistic sample. For the preliminary results drawn from the non-autistic group only (and which featured in the Stage 1 version of this report) see “Results from the non-autistic sample – Preregistered analyses” in the Supplementary Materials.

To be comparable to the data collected from this control group, we aimed to collect complete datasets from at least 100 autistic people (see our Power analysis section for considerations on potential data loss). During data collection, it was discovered that a number of recruited individuals were suspected to be fraudulent participants: this was due to an autism organization sharing the online link to take part in the study directly without having to contact the research team. Data gathered during this period of recruitment is not included in the study as a high number of participants’ emails and addresses (collected for reimbursement purposes) were deemed to be suspicious. This unfortunately had a knock on effect on our ability to meet out intended recruitment target, due to resource constraints. In the end, we successfully collected 80 autistic data sets. Even when outliers were removed, we achieved our minimum power requirements for 73 autistic datasets for each regression conducted.

@@

Table 1 summarises the participants’ characteristics.

@@

The Hospital Anxiety and Depression scale [HADS, @zigmond1983a] consists of seven questions for anxiety and seven questions for depression. Depression and anxiety scales are scored separately. The HADS has been shown to perform well in measuring anxiety and depression symptoms in non-clinical samples as well as clinical samples [@bjelland2002a], including the identification of anxiety and depression in autistic individuals, with good internal consistency and convergent validity for both the anxiety and depression scales [@uljarevic2013a]. The means, standard deviations and distribution of the HADS data for our data from typically developed adults confirm the measure is normally distributed, with suitable variation in scores that will allow for the exploration of the impacts of anxiety and depression on our variables of interest. For  HADS anxiety, M = 10.87 (SD = 2.90). For HADS depression, M = 8.69 (SD = 1.94).

@@

Our first sample of non-autistic participants was a sample of 98 participant, (7 of which were considered outliers in our preliminary analyses). We intended to collect at least 100 complete datasets from our autistic sample, and at least 90 datasets that survive removal due to attention check fails, being an outlier, or poor function fit. As noted in our Participants section above, were were unable to achieve this, but our final sample was 178 participants, after removing incomplete datasets and individuals who failed the attention check. This sample size should still negate any issues with multi-collinearity, and inflation of previous estimate due to publication bias. As previously noted, we included those who self-identify as autistic in our autistic sample in order to aid in recruiting our goal of at least 100 participants. Also, we did not formally checking participants for their clinical diagnosis: as we cannot verify who has a formal diagnosis of autism, we felt it practical to allow people who self-identify as autistic to take part and just ask them if they are or are not formally diagnosed.

@@

@@

In our first series of regressions, a continuous measure of autistic traits, the AQ28, was entered in the final step. Table 3 summarises the results of this regression series. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1s and 2 (although the addition of the TAS in step 2 did not lead to a significant increase in the variance explained). The only significant predictor was gender, specifically the dummy variable indicating “other” gender. See sub-section “The role of gender” for follow up tests on gender effects on emotion PSE. Table 4 summarises the coefficients for the regressions with significant models.

>>>>

packagelist <- c('pwr','rstatix','kableExtra','MASS','lm.beta')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

knitr::opts_chunk$set(echo = FALSE, include=TRUE)

@@

TD <- subset(data,Group_NTorASC==0)
ASC <- subset(data,Group_NTorASC==1)

cookthresh <- 0.022

```{r regseries1}

# stepwise regression series 1

# Emotion Attribution DV
#define model with all predictors
all <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EA <- data[i,]

# intercept only (null) model
EAmodel0 <- lm(EMOATTINV ~ 1, data=data_EA)

# first stepwise entry
EAmodel1 <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EA)

# second stepwise entry
EAmodel2 <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EA)

# third stepwise entry
EAmodel3 <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EA)

# fourth stepwise entry
EAmodel4 <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data_EA)

# Identity Attribution DV
#define model with all predictors
all <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IA <- data[i,]

# intercept only (null) model
IAmodel0 <- lm(IDATTINV ~ 1, data=data_IA)

# first stepwise entry
IAmodel1 <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IA)

# second stepwise entry
IAmodel2 <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IA)

# third stepwise entry
IAmodel3 <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IA)

# fourth stepwise entry
IAmodel4 <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data_IA)

# Emotion PSE DV
#define model with all predictors
all <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EP <- data[i,]

# intercept only (null) model
EPmodel0 <- lm(EMOPSE ~ 1, data=data_EP)

# first stepwise entry
EPmodel1 <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EP)

# second stepwise entry
EPmodel2 <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EP)

# third stepwise entry
EPmodel3 <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EP)

# fourth stepwise entry
EPmodel4 <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data_EP)

# Identity PSE DV
#define model with all predictors
all <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IP <- data[i,]

# intercept only (null) model
IPmodel0 <- lm(IDPSE ~ 1, data=data_IP)

# first stepwise entry
IPmodel1 <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IP)

# second stepwise entry
IPmodel2 <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IP)

# third stepwise entry
IPmodel3 <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IP)

# fourth stepwise entry
IPmodel4 <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + AQ, data=data_IP)

@@

The non-autistic group was recruited via social media, ‘word of mouth’, and via Prolific. We aimed to collect 100 non-autistic participants, and had 119 complete datasets. However, 21 were removed due to being incomplete, or failing an attention check measure. This means that data from a sample of `r nrow(TD)` non-autistic adults was been collected in a previous study using the same methods, materials and experimental design. This sample serves as a comparison group to the autistic sample. For the preliminary results drawn from the non-autistic group only (and which featured in the Stage 1 version of this report) see “Results from the non-autistic sample – Preregistered analyses” in the Supplementary Materials.

To be comparable to the data collected from this control group, we aimed to collect complete datasets from at least 100 autistic people (see our Power analysis section for considerations on potential data loss). During data collection, it was discovered that a number of recruited individuals were suspected to be fraudulent participants: this was due to an autism organization sharing the online link to take part in the study directly without having to contact the research team. Data gathered during this period of recruitment is not included in the study as a high number of participants’ emails and addresses (collected for reimbursement purposes) were deemed to be suspicious. This unfortunately had a knock on effect on our ability to meet out intended recruitment target, due to resource constraints. In the end, we successfully collected `r nrow(ASC)` autistic data sets. Even when outliers were removed, we achieved our minimum power requirements for 73 autistic datasets for each regression conducted.

@@

Table \@ref(tab:table1) summarises the participants’ characteristics.

``` {r table1}

table1data <- data.frame(matrix(0,nrow=20,ncol=4))

table1data[1,] <- c('','Full Sample','Autistic Sample','Non-autistic Sample')
table1data[2,] <- c('',paste0('(N = ',nrow(data),')'),paste0('(N = ',nrow(ASC),')'),paste0('(N = ',nrow(TD),')'))
table1data[3,] <- c('Gender',paste0('N Female = ',sum(data$GENDER=='Fema')),paste0('N Female = ',sum(ASC$GENDER=='Fema')),paste0('N Female = ',sum(TD$GENDER=='Fema')))
table1data[4,] <- c('',paste0('N Male = ',sum(data$GENDER=='Male')),paste0('N Male = ',sum(ASC$GENDER=='Male')),paste0('N Male = ',sum(TD$GENDER=='Male')))
table1data[5,] <- c('',paste0('N Other = ',sum(data$GENDER=='Othe')),paste0('N Other = ',sum(ASC$GENDER=='Othe')),paste0('N Other = ',sum(TD$GENDER=='Othe')))
table1data[7,] <- c('Age',paste0(round(mean(data$AGE),digits=2),' (',round(sd(data$AGE),digits=2),')'),paste0(round(mean(ASC$AGE),digits=2),' (',round(sd(ASC$AGE),digits=2),')'),paste0(round(mean(TD$AGE),digits=2),' (',round(sd(TD$AGE),digits=2),')'))
table1data[9,] <- c('Ethnicity',paste0('N Asian = ',sum(data$ETHNCITY=='Asian')),paste0('N Asian = ',sum(ASC$ETHNCITY=='Asian')),paste0('N Asian = ',sum(TD$ETHNCITY=='Asian')))
table1data[10,] <- c('',paste0('N Black = ',sum(data$ETHNCITY=='Black')),paste0('N Black = ',sum(ASC$ETHNCITY=='Black')),paste0('N Mixed = ',sum(TD$ETHNCITY=='mixed')))
table1data[11,] <- c('',paste0('N Mixed = ',sum(data$ETHNCITY=='mixed')),paste0('N Mixed = ',sum(ASC$ETHNCITY=='mixed')),paste0('N White = ',sum(TD$ETHNCITY=='White')))
table1data[12,] <- c('',paste0('N White = ',sum(data$ETHNCITY=='White')),paste0('N White = ',sum(ASC$ETHNCITY=='White')),'')
table1data[14,] <- c('HADS-Depression',paste0(round(mean(data$HDEP7),digits=2),' (',round(sd(data$HDEP7),digits=2),')'),paste0(round(mean(ASC$HDEP7),digits=2),' (',round(sd(ASC$HDEP7),digits=2),')'),paste0(round(mean(TD$HDEP7),digits=2),' (',round(sd(TD$HDEP7),digits=2),')'))
table1data[16,] <- c('HADS-Anxiety',paste0(round(mean(data$HANX7),digits=2),' (',round(sd(data$HANX7),digits=2),')'),paste0(round(mean(ASC$HANX7),digits=2),' (',round(sd(ASC$HANX7),digits=2),')'),paste0(round(mean(TD$HANX7),digits=2),' (',round(sd(TD$HANX7),digits=2),')'))
table1data[18,] <- c('AQ-28',paste0(round(mean(data$AQ),digits=2),' (',round(sd(data$AQ),digits=2),')'),paste0(round(mean(ASC$AQ),digits=2),' (',round(sd(ASC$AQ),digits=2),')'),paste0(round(mean(TD$AQ),digits=2),' (',round(sd(TD$AQ),digits=2),')'))
table1data[20,] <- c('TAS-20',paste0(round(mean(data$TASTOTAL),digits=2),' (',round(sd(data$TASTOTAL),digits=2),')'),paste0(round(mean(ASC$TASTOTAL),digits=2),' (',round(sd(ASC$TASTOTAL),digits=2),')'),paste0(round(mean(TD$TASTOTAL),digits=2),' (',round(sd(TD$TASTOTAL),digits=2),')'))
table1data[c(6,8,13,15,17,19),] <- ''

knitr::kable(table1data, booktabs = T, col.names = NULL, caption='Participant Characteristics.', align='llll') %>%
  row_spec(2, hline_after=T) %>%
  kable_styling(latex_options='HOLD_position') %>%
  add_footnote('For non-category data, statistics reported are means with standard deviations in parentheses.',notation='none')

@@

The Hospital Anxiety and Depression scale [HADS, @zigmond1983a] consists of seven questions for anxiety and seven questions for depression. Depression and anxiety scales are scored separately. The HADS has been shown to perform well in measuring anxiety and depression symptoms in non-clinical samples as well as clinical samples [@bjelland2002a], including the identification of anxiety and depression in autistic individuals, with good internal consistency and convergent validity for both the anxiety and depression scales [@uljarevic2013a]. The means, standard deviations and distribution of the HADS data for our data from typically developed adults confirm the measure is normally distributed, with suitable variation in scores that will allow for the exploration of the impacts of anxiety and depression on our variables of interest. For HADS anxiety, M = `r round(mean(TD$HANX7),digits=2)` (SD = `r round(sd(TD$HANX7),digits=2)`). For HADS depression, M = `r round(mean(TD$HDEP7),digits=2)` (SD = `r round(sd(TD$HDEP7),digits=2)`).

@@

Our first sample of non-autistic participants was a sample of `r nrow(TD)` participants, (7 of which were considered outliers in our preliminary analyses). We intended to collect at least 100 complete datasets from our autistic sample, and at least 90 datasets that survive removal due to attention check fails, being an outlier, or poor function fit. As noted in our Participants section above, were were unable to achieve this, but our final sample was `r nrow(data)` participants, after removing incomplete datasets and individuals who failed the attention check. This sample size should still negate any issues with multi-collinearity, and inflation of previous estimate due to publication bias. As previously noted, we included those who self-identify as autistic in our autistic sample in order to aid in recruiting our goal of at least 100 participants. Also, we did not formally checking participants for their clinical diagnosis: as we cannot verify who has a formal diagnosis of autism, we felt it practical to allow people who self-identify as autistic to take part and just ask them if they are or are not formally diagnosed.

@@

``` {r table2, warning=FALSE}

table2data <- data.frame(matrix(0,nrow=14,ncol=9))

table2data[,1] <- c('','','','TAS-TOTAL','','','AQ','','','HADS Depression','','','HADS Anxiety','')
table2data[c(6,9,12),] <- ''
table2data[1,] <- c('','','','', '','', '', 'Emotion', 'Identity')
table2data[2,] <- c('','TAS-','AQ','HADS', 'HADS','Emotion PSE', 'Identity PSE', 'attribution', 'attribution')
table2data[3,] <- c('','TOTAL','','Depression','Anxiety',paste0('(N=',nrow(data_EP),')'),paste0('(N=',nrow(data_IP),')'),paste0('(N=',nrow(data_EA),')'),paste0('(N=',nrow(data_IA),')'))
table2data[4:5,2] <- ''
table2data[7:8,3] <- ''
table2data[10:11,4] <- ''
table2data[13:14,5] <- ''

cout <- cor.test(data$TASTOTAL,data$AQ,method='spearman',alternative='greater')
table2data[7,2] <- p_format(cout$estimate,digits=3,leading.zero=F)
table2data[8,2] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)
table2data[4,3] <- p_format(cout$estimate,digits=3,leading.zero=F)
table2data[5,3] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data$TASTOTAL,data$HDEP7,method='spearman',alternative='greater')
table2data[10,2] <- p_format(cout$estimate,digits=2,leading.zero=F)
table2data[11,2] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)
table2data[4,4] <- p_format(cout$estimate,digits=2,leading.zero=F)
table2data[5,4] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data$TASTOTAL,data$HANX7,method='spearman',alternative='less')
table2data[13,2] <- round(cout$estimate,digits=3)
table2data[14,2] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)
table2data[4,5] <- round(cout$estimate,digits=3)
table2data[5,5] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data$AQ,data$HDEP7,method='spearman',alternative='greater')
table2data[10,3] <- p_format(cout$estimate,digits=3,leading.zero=F)
table2data[11,3] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)
table2data[7,4] <- p_format(cout$estimate,digits=3,leading.zero=F)
table2data[8,4] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data$AQ,data$HANX7,method='spearman',alternative='less')
table2data[13,3] <- round(cout$estimate,digits=3)
table2data[14,3] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)
table2data[7,5] <- round(cout$estimate,digits=3)
table2data[8,5] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data$HDEP7,data$HANX7,method='spearman',alternative='less')
table2data[13,4] <- round(cout$estimate,digits=3)
table2data[14,4] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)
table2data[10,5] <- round(cout$estimate,digits=3)
table2data[11,5] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EP$EMOPSE,data_EP$TASTOTAL,method='spearman',alternative='greater')
table2data[4,6] <- round(cout$estimate,digits=3)
table2data[5,6] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EP$EMOPSE,data_EP$AQ,method='spearman',alternative='greater')
table2data[7,6] <- round(cout$estimate,digits=3)
table2data[8,6] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EP$EMOPSE,data_EP$HDEP7,method='spearman',alternative='greater')
table2data[10,6] <- round(cout$estimate,digits=3)
table2data[11,6] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EP$EMOPSE,data_EP$HANX7,method='spearman',alternative='greater')
table2data[13,6] <- round(cout$estimate,digits=3)
table2data[14,6] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IP$IDPSE,data_IP$TASTOTAL,method='spearman',alternative='greater')
table2data[4,7] <- round(cout$estimate,digits=3)
table2data[5,7] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IP$IDPSE,data_IP$AQ,method='spearman',alternative='greater')
table2data[7,7] <- round(cout$estimate,digits=3)
table2data[8,7] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IP$IDPSE,data_IP$HDEP7,method='spearman',alternative='greater')
table2data[10,7] <- round(cout$estimate,digits=3)
table2data[11,7] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IP$IDPSE,data_IP$HANX7,method='spearman',alternative='greater')
table2data[13,7] <- round(cout$estimate,digits=3)
table2data[14,7] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EA$EMOATTINV,data_EA$TASTOTAL,method='spearman',alternative='greater')
table2data[4,8] <- round(cout$estimate,digits=3)
table2data[5,8] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EA$EMOATTINV,data_EA$AQ,method='spearman',alternative='greater')
table2data[7,8] <- round(cout$estimate,digits=3)
table2data[8,8] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EA$EMOATTINV,data_EA$HDEP7,method='spearman',alternative='less')
table2data[10,8] <- round(cout$estimate,digits=3)
table2data[11,8] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_EA$EMOATTINV,data_EA$HANX7,method='spearman',alternative='less')
table2data[13,8] <- round(cout$estimate,digits=3)
table2data[14,8] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IA$IDATTINV,data_IA$TASTOTAL,method='spearman',alternative='greater')
table2data[4,9] <- round(cout$estimate,digits=3)
table2data[5,9] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IA$IDATTINV,data_IA$AQ,method='spearman',alternative='greater')
table2data[7,9] <- round(cout$estimate,digits=3)
table2data[8,9] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IA$IDATTINV,data_IA$HDEP7,method='spearman',alternative='less')
table2data[10,9] <- round(cout$estimate,digits=3)
table2data[11,9] <- p_format(cout$p.value,digits=2,accuracy=0.001,leading.zero=F,add.p=T)

cout <- cor.test(data_IA$IDATTINV,data_IA$HANX7,method='spearman',alternative='less')
table2data[13,9] <- round(cout$estimate,digits=3)
table2data[14,9] <- p_format(cout$p.value,digits=3,accuracy=0.001,leading.zero=F,add.p=T)

knitr::kable(table2data, booktabs = T, col.names = NULL, caption='Correlations between alexithymia traits, autistic traits, depression and anxiety symptoms and face processing variables.', align='lllllllll') %>%
  row_spec(3, hline_after=T) %>%
  kable_styling(latex_options='HOLD_position',font_size=8) %>%
  add_footnote('All correlations are Spearman’s Rank and one-tailed. Note that correlations with the face processing variables are with outliers removed, as per Cook’s Distance threshold rules, generated for regression series 1 (AQ in final step).', notation='none')

@@

In our first series of regressions, a continuous measure of autistic traits, the AQ28, was entered in the final step. Table \@ref(tab:table3) summarises the results of this regression series. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1s and 2 (although the addition of the TAS in step 2 did not lead to a significant increase in the variance explained). The only significant predictor was gender, specifically the dummy variable indicating “other” gender. See sub-section “The role of gender” for follow up tests on gender effects on emotion PSE. Table 4 summarises the coefficients for the regressions with significant models.

``` {r table3}

table3data <- data.frame(matrix(0,nrow=6,ncol=9))

table3data[1,] <- c('','','F change,','','F change,','','F change,','','F change,')
table3data[2,] <- c('','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value')
table3data[,1] <- c('','','Model 1','Model 2','Model 3','Model 4')

a <- summary(EAmodel1)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[3,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel2)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[4,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel3)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[5,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel4)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[6,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel1)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[3,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel2)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[4,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel3)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[5,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel4)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[6,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel1)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table3data[3,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel2)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table3data[4,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel3)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table3data[5,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel4)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table3data[6,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel1)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[3,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel2)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[4,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel3)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[5,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel4)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table3data[6,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- anova(EAmodel0,EAmodel1)
table3data[3,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel1,EAmodel2)
table3data[4,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel2,EAmodel3)
table3data[5,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel3,EAmodel4)
table3data[6,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel0,IAmodel1)
table3data[3,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel1,IAmodel2)
table3data[4,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel2,IAmodel3)
table3data[5,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel3,IAmodel4)
table3data[6,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel0,EPmodel1)
table3data[3,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel1,EPmodel2)
table3data[4,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel2,EPmodel3)
table3data[5,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel3,EPmodel4)
table3data[6,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel0,IPmodel1)
table3data[3,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel1,IPmodel2)
table3data[4,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel2,IPmodel3)
table3data[5,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))
